### 2020-05-28 report/sections/introduction/contributions.tex
Report: notes on part 1

\paragraph{Note: from PLACES}

We present a workflow for developing type-safe interactive SPAs motivated by the MPST framework:

\begin{enumerate}
\item An endpoint API code generation workflow targeting TypeScript-based web applications for multiparty sessions;
\item An encoding of session types in server-side TypeScript that enforces static linearity;
\item An encoding of session types in browser-side TypeScript using the React framework that guarantees affine usage of communication channels.
\end{enumerate}

>>>>

We present \dots

\paragraph{\cref{part:server}} \dots

\paragraph{\cref{part:general}} \dots

\paragraph{\cref{part:evalconcl}} \dots
